Leveraged Volume Sampling - Summary

### 2019-03-02 summary/paper-summary.tex
wip - lev. vol sampling section

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}

@@

>>>>

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}

@@

        Furthermore, using a bit of algebra, the paper shows that for \textit{Rescaled Volume Sampling}:
        \begin{equation}
            E(Q_{\pi}) = (k-d)I + diag(\frac{l_{1}}{q_{1}}, \hdots, \frac{l_{n}}{q_{n}})
        \end{equation}

    \section{Leveraged Volume Sampling}
        \textit{Leveraged Volume Sampling} is \textit{Rescaled Volume Sampling} where $q_{i}=\frac{l_{i}}{d}$ (note that $\sum_{i=1}^{n}l_{i}=d$).
        This procedure is unbiased (as it is a case of \textit{Rescaled Volume Sampling}) and is subject to favorable tail bounds (more on that in the next section).
        You can poll such a subset with an algorithm named \textit{Determinantal Rejection Sampling} which selects $k$ lines from $X$ that boils down to the following steps:
        \begin{itemize}
            \item Set $s \coloneqq max(k, 4d^{2})$.
            \item Repeat until acceptance selection of lines $\pi$ of size $s$ i.i.d from $1..n$ and accept with probability $\frac{det(\frac{1}{s}X^{T}Q_{\pi}X)}{det(X^{T}X)}$.
            \item Use \textit{Volume Sampling} to reduce the selected $s$ rows to $k$ rows.
        \end{itemize}

        The proof that this procedure indeed yields a \textit{Leveraged Volume Sampling} distributed set is largely due to the fact that when you
        select a \textit{Leveraged Volume Sampling} distributed set of size $s$ and then apply \textit{Reverse Iterative Volume Sampling} to sub-select
        a $k$ sized subset then the \textit{Leveraged Volume Sampling} distribution is recursively maintained at each step.
